DATA 621 Homework #3

### 2019-10-29 hw3/HW3.Rmd
More work on HW3

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(kableExtra)
library(corrplot)
library(caret)
library(Amelia)
# Thank you Stack Overflow!
# A Prefix nulling hook.

@@

## Data Preparation

```{r}
baseline <- glm(target ~ nox, family = binomial(link = "logit"), train)
summary(baseline)
test$baseline <- ifelse(predict(baseline, test) < 0.5, 0, 1)
test$baseline2 <- predict(baseline, test)
confusionMatrix(factor(test$baseline), factor(test$target))
```

@@

for (i in 1:6){
  p <- plot(fit, data = "test", tree=i)
  print(p)
}

```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment=NA, message=FALSE, warning=FALSE)
library(tidyverse)
library(kableExtra)
library(corrplot)
library(caret)
library(rpart)
library(rpart.plot)
library(Amelia)
# Thank you Stack Overflow!
# A Prefix nulling hook.

@@

## Data Preparation
```{r}
ggplot(train, aes(rad , nox, color=as.factor(target))) +
  geom_point()
```

@@

for (i in 1:6){
  p <- plot(fit, data = "test", tree=i)
  print(p)
}
```

```{r}
fit <- rpart(target ~ ., method="class", data=train)
rpart.plot(fit)
```

```{r}
get_high_nox <- function(x){
  if(x > 0.53){
    return("High")
  } else {
    return("Low")
  }
}

get_divider <- function(x, y){
  if(x < 10 & y < 0.6){
    return(1)
  } else {
    return(0)
  }
}

train <- train %>%
  rowwise() %>%
  mutate(high_nox = get_high_nox(nox),
         divider = get_divider(rad, nox))

test <- test %>%
  rowwise() %>%
  mutate(high_nox = get_high_nox(nox),
         divider = get_divider(rad, nox))
```

```{r}
baseline <- glm(target ~ nox, family = binomial(link = "logit"), train)
summary(baseline)
test$baseline <- ifelse(predict(baseline, test) < 0.5, 0, 1)
test$baseline_yhat <- predict(baseline, test)
confusionMatrix(factor(test$baseline), factor(test$target))
```

```{r}
model1 <- glm(target ~ high_nox + indus, family = binomial(link = "logit"), train)
summary(model1)
test$model1 <- ifelse(predict(model1, test) < 0.5, 0, 1)
test$model1_yhat <- predict(model1, test)
confusionMatrix(factor(test$model1), factor(test$target))
```

```{r}
model2 <- glm(target ~ divider, family = binomial(link = "logit"), train)
summary(model2)
test$model2 <- ifelse(predict(model2, test) < 0.5, 0, 1)
test$model2_yhat <- predict(model2, test)
confusionMatrix(factor(test$model2), factor(test$target))
```
